Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-03-01 main_paper.tex
Correct a Citation
Remove application section for now (see a37f881)

The RD design strategy was introduced by \cite{thistlethwaite1960} to study
educational outcomes, and many of its first recent applications in economics
were to estimate the effects of other educational policies: evaluating the
impact of investments in school facilities, class sizes, remedial education,
early childhood education, and financial aid effects on student achievement and
later outcomes, for example.\footnote{%
  See, for example, \cite{vdk2002}, \cite{jacoblefgren2004}, \cite{ludwig2007},
  \cite{urquiola2009}, \cite{cellini2010}} %
But the underlying identification strategy has proven to apply much more widely
and RD has been used in health economics;\footnote{%
  \cite{Card2009,barreca2011saving}} %
political science, providing evidence regarding incumbency advantage in
elections, electoral enfranchising and policy changes associated with the
introduction of electronic voting, strategic voting behavior, and local media
effects and ad expenditure in presidential elections in the U.S.\footnote{%
  \cite{lee2008}, \cite{Caughey2011}, \cite{keele2014geographic},
  \cite{erikson2015}, \cite{Fujiwara2011,Fujiwara2015}}, %
among other fields. \cite{imbens2008} and \cite{lee2010} provide recent
overviews of this literature with many more examples.

@@

The paper is organized as follows. Section~\ref{background} describes the basic
RD approach, its usual implementation, and the explicit analytical bias
correction approach in the literature. Section~\ref{boot} presents our proposed
bootstrap bias corrected RD algorithm and discusses its asymptotic
properties. Simulation evidence that the bootstrap procedure provides valid CIs
and its relative performance to the analytical bias correction are presented in
Section~\ref{sim}, and Section~\ref{application} demonstrates the estimator's
usage by applying it to the Head Start dataset used by~\cite{ludwig2007}.
Finally, Section~\ref{conclusion} concludes.

@@

\section{Application}\label{application}

In this section, we apply the bootstrap procedure to the data\footnote{The data is publicly available from http://faculty.econ.ucdavis.edu/faculty/dlmiller/statafiles/.} used in \cite{ludwig2007}. In their paper, the effects of Head Start application assistance on federal spending, mortality and education attainment were investigated under standard RD design. They utilized the fact that grant-writing assistance were offered only to the poorest 300 counties to identify the average treatment effect (ATE) at the cutoff.

We estimate the ATE with alternative procedures and compare the new estimates with results in \cite{ludwig2007}. Bias-corrected point estimates and robust confidence intervals are reported. For completeness, we also include results following the procedure proposed by CCT. In \cite{ludwig2007}, analytical standard error and percentile-T bootstrapped p-value were reported\footnote{However, we were unable to reproduce their point estimates for the ATE under the nonparametric setting using triangular kernel, which was documented in their paper. Instead, we used uniform kernel and obtained exactly the same results as theirs.}. The procedure proposed by CCT provides analytical standard error and confidence interval. Our bootstrap procedure provides standard error and confidence interval from the bootstrap distribution. In both CCT and bootstrap procedures, we set $p = 1$, $q = 2$ and used uniform kernel. In the bootstrap procedure, we used 500 bootstraps for bias correction and 999 for confidence interval.

These results are shown in Table \ref{tab: head start spending}-\ref{tab: education 2000 ages 25-34}. We find that (1) the choice of bandwidth may significantly affect estimated ATE and its significance level; (2) the optimal bandwidths following CCT procedure are much smaller than actually being used in \cite{ludwig2007} and (3) our bootstrap procedure produces similar results to CCT.

\begin{table}[ht]
	\centering
	\begin{tabular}{cccccc}
		\toprule
		& \multicolumn{3}{c}{LM 2007} & CCT 2014 & Bootstrap \\
		\midrule
		& \multicolumn{5}{c}{Panel A: 1968 Head Start spending per child} \\
		Bandwidth & 9 & 18 & 36 & 5.414, 10.175 & 5.414, 10.175 \\
		Effect    & 137.251 & 114.711 & 134.491 & 143.811 & 148.990 \\
		SE        & 128.968 & 91.267  & 62.593 & 113.404 & 182.729 \\
		p-value   & 0.157   & 0.138   & 0.045  & & \\
		95\% CI   & & & & (-78.457 366.078) & (-179.120  547.755) \\

		&&&&& \\
		& \multicolumn{5}{c}{Panel B: 1972 Head Start spending per child} \\
		Bandwidth & 9 & 18 & 36 & 5.034, 12.020 & 5.034, 12.020 \\
		Effect    & 182.119 & 88.959 & 130.153 & 94.260 & 100.404 \\
		SE        & 148.321 & 101.697 & 67.613 & 122.224 & 196.008 \\
		p-value   & 0.085   & 0.352   & 0.090  & & \\
		95\% CI   & & & & (-145.294 333.814) & (-165.816 622.976) \\

		&&&&& \\
		& \multicolumn{5}{c}{Panel C: 1972 other social spending per capita} \\
		Bandwidth & 9 & 18 & 36 & 4.612, 8.461 & 4.612, 8.461 \\
		Effect    & 14.474 & 19.590 & 14.506 & 15.418 & 15.857 \\
		SE        & 28.356 & 19.612 & 14.929 & 29.041 & 39.902 \\
		p-value   & 0.459   & 0.222   & 0.478  & & \\
		95\% CI   & & & & (-41.501 72.337) & (-64.153 91.999) \\
		\bottomrule
	\end{tabular}
	\caption{The effect of Head Start assistance on Head Start spending. The first three columns come from Table 2 in \cite{ludwig2007}.}
	\label{tab: head start spending}
\end{table}

\begin{table}[ht]
	\centering
	\begin{tabular}{cccccc}
		\toprule
		& \multicolumn{3}{c}{LM 2007} & CCT 2014 & Bootstrap \\
		\midrule
		Bandwidth & 9 & 18 & 36 & 3.888, 6.807 & 3.888, 6.807 \\
		Effect    & -1.895 & -1.198 & -1.114 & -3.795 & -3.852 \\
		SE        & 0.980 & 0.796  & 0.544 & 1.654 & 1.526 \\
		p-value   & 0.036   & 0.081   & 0.027  & & \\
		95\% CI   & & & & (-7.037 -0.554) & (-6.565 -0.578) \\
		\bottomrule
	\end{tabular}
	\caption{The effect of Head Start assistance on mortality. The first three columns come from Table 3 in \cite{ludwig2007}.}
	\label{tab: mortality}
\end{table}

\begin{table}[ht]
	\centering
	\begin{tabular}{cccc}
		\toprule
		& LM 2007 & CCT 2014 & Bootstrap \\
		\midrule
		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
		Bandwidth & 7 & 3.671, 8.618 & 3.671, 8.618 \\
		Effect    & 0.030 & 0.055 & 0.054 \\
		SE        & 0.016 & 0.021 & 0.021 \\
		p-value   & 0.032 & & \\
		95\% CI        & & (0.014 0.096) & (0.010 0.094) \\

		&&& \\
		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
		Bandwidth & 7 & 5.076, 10.251 & 5.076, 10.251 \\
		Effect    & 0.037 & 0.051 & 0.051 \\
		SE        & 0.020 & 0.024 & 0.024 \\
		p-value   & 0.031 & & \\
		95\% CI        & & (0.004 0.099) & (0.001 0.092) \\
		\bottomrule
	\end{tabular}
	\caption{The effect of Head Start assistance on education (1990, ages 18-24). The first column is result for directly treated cohorts (1990, ages 18-24) in Table 4 in \cite{ludwig2007}.}
	\label{tab: education 1990 ages 18-24}
\end{table}

\begin{table}[ht]
	\centering
	\begin{tabular}{cccc}
		\toprule
		& LM 2007 & CCT 2014 & Bootstrap \\
		\midrule
		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
		Bandwidth & 7 & 4.837, 9.85 & 4.837, 9.85 \\
		Effect    & 0.000 & 0.014 & 0.013 \\
		SE        & 0.016 & 0.019 & 0.019 \\
		p-value   & 0.974 & & \\
		CI        & & (-0.024 0.051) & (-0.026 0.051) \\

		&&& \\
		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
		Bandwidth & 7 & 5.382, 10.621 & 5.382, 10.621 \\
		Effect    & 0.028 & 0.033 & 0.032 \\
		SE        & 0.019 & 0.023 & 0.022 \\
		p-value   & 0.017 & & \\
		CI        & & (-0.014 0.079) & (-0.009 0.077)\\
		\bottomrule
	\end{tabular}
	\caption{The effect of Head Start assistance on education (2000, ages 18-24). The first column is result for directly treated cohorts (2000, ages 18-24) in Table 4 in \cite{ludwig2007}.}
	\label{tab: education 2000 ages 18-24}
\end{table}

\begin{table}[ht]
	\centering
	\begin{tabular}{cccc}
		\toprule
		& LM 2007 & CCT 2014 & Bootstrap \\
		\midrule
		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
		Bandwidth & 7 & 6.074, 11.477 & 6.074, 11.477 \\
		Effect    & 0.006 & 0.014 & 0.014 \\
		SE        & 0.014 & 0.015 & 0.015 \\
		p-value   & 0.666 & & \\
		CI        & & (-0.014 0.043) & (-0.023 0.036) \\

		&&& \\
		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
		Bandwidth & 7 & 5.509, 11.463 & 5.509, 11.463 \\
		Effect    & 0.040 & 0.049 & 0.049 \\
		SE        & 0.017 & 0.020 & 0.021 \\
		p-value   & 0.009 & & \\
		CI        & & (0.010 0.089) & (0.003 0.083) \\
		\bottomrule
	\end{tabular}
	\caption{The effect of Head Start assistance on education (2000, ages 25-34). The first column is result for directly treated cohorts (2000, ages 25-34) in Table 4 in \cite{ludwig2007}.}
	\label{tab: education 2000 ages 25-34}
\end{table}

>>>>

The RD design strategy was introduced by \cite{thistlethwaite1960} to study
educational outcomes, and many of its first recent applications in economics
were to estimate the effects of other educational policies: evaluating the
impact of investments in school facilities, class sizes, remedial education,
early childhood education, and financial aid effects on student achievement and
later outcomes, for example.\footnote{%
  See, for example, \cite{vdk2002}, \cite{jacoblefgren2004}, \cite{ludwig2007},
  \cite{urquiola2009}, \cite{cellini2010}} %
But the underlying identification strategy has proven to apply much more widely
and RD has been used in health economics;\footnote{%
  \cite{Card2009,barreca2011saving}} %
political science, providing evidence regarding incumbency advantage in
elections, electoral enfranchising and policy changes associated with the
introduction of electronic voting, strategic voting behavior, and local media
effects and ad expenditure in presidential elections in the U.S.\footnote{%
  \cite{lee2008}, \cite{caughey2011elections}, \cite{keele2014geographic},
  \cite{erikson2015}, \cite{Fujiwara2011,Fujiwara2015}}, %
among other fields. \cite{imbens2008} and \cite{lee2010} provide recent
overviews of this literature with many more examples.

@@

The paper is organized as follows. Section~\ref{background} describes the basic
RD approach, its usual implementation, and the explicit analytical bias
correction approach in the literature. Section~\ref{boot} presents our proposed
bootstrap bias corrected RD algorithm and discusses its asymptotic
properties. Simulation evidence that the bootstrap procedure provides valid CIs
and its relative performance to the analytical bias correction are presented in
Section~\ref{sim}.
Finally, Section~\ref{conclusion} concludes.

@@
